;==============================================================
;
; nimble_orders.ltx
;	CoC 1.5b r4 - DoctorX Call of The Zone 1.0
;
;	Modified by: DoctorX (activated Nimble as trader)
;	Last revised: September 19, 2017
;
;==============================================================


; This plugin determines and configures how Nimble's order system works.
; Available items are handled here if using the standard CoP-style system.
; If acting as a trader, supplies can be modified in configs/misc/trade/trade_loner_nimble.ltx

[settings]
item_count = 10


;//////////////////////////////////////////////////////////////////////////////////////////////////
;
; Nimble As Trader
;
;	Modified by DoctorX
;	for DoctorX Call of The Zone 1.0
;	September 19, 2017
;
;--------------------------------------------------------------------------------------------------

 nimble_trade_instead = false
;nimble_trade_instead = true

; \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\


[item_count]
category_1 = 3
category_2 = 3
category_3 = 3
category_4 = 1
category_5 = 1
category_6 = 1
category_7 = 1
category_8 = 1
category_9 = 1
category_10 = 1

; Usage: Prepay (Agreed), Prepay (Refused), Cost.
[costs_table]
category_1 = 700, 1400, 2800
category_2 = 2000, 4000, 8000
category_3 = 4000,8000, 16000
category_4 = 4000,8000, 16000
category_5 = 8000,16000, 32000
category_6 = 6000,12000, 24000
category_7 = 12000, 24000, 48000
category_8 = 12000, 24000, 48000
category_9 = 12000, 24000, 48000
category_10 = 12000, 24000, 48000

; Potential items which can be received depending on selection.
; Multiple items can be given at once if you separate them with a comma.

; Pistols.
[buy_item_table_1]
item1 = wpn_desert_eagle_nimble
item2 = wpn_sig220_nimble
item3 = wpn_usp_nimble

; Sub-machine guns.
[buy_item_table_2]
item1 = wpn_mp5_nimble
item2 = wpn_spas12_nimble
item3 = wpn_protecta_nimble

; Assault rifles.
[buy_item_table_3]
item1 = wpn_groza_nimble
item2 = wpn_g36_nimble
item3 = wpn_fn2000_nimble

; Sniper rifles.
[buy_item_table_4]
item1 = wpn_vintorez_nimble


; Headgear.
[buy_item_table_5]
item1 = helm_hardhat, cs_heavy_outfit

; Scientific outfits.
[buy_item_table_6]
item1 = scientific_outfit

; Exoskeleton outfits.
[buy_item_table_7]
item1 = exo_outfit

[buy_item_table_8]
item1 = ammo_5.56x45_ap, ammo_5.56x45_ap, ammo_5.56x45_ap, ammo_5.56x45_ap

[buy_item_table_9]
item1 = wpn_svu_nimble

[buy_item_table_10]
item1 = wpn_svu_nimble
